\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex
removing comment

\kris{TODO: FIX THIS (make consistent w semantics)}
\[\small
\begin{array}{ccc}
  {\color{brown}
    \inferrule[\textsc{Fac-Create-Pos}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{+ \ell \in pc} \\\\
                e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  & 
  {\color{gray}
    \inferrule[\textsc{Fac-Create-Neg}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{- \ell \in pc} \\\\
                e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  &
  {\color{purple}
    \inferrule[\textsc{Fac-Create-Split}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{\{+\ell, -\ell\} \cap pc = \varnothing} \\\\
                e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
                e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
                v = \formfacet{pc}{v_1}{v_2}}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}

\end{array}
\]

>>>>

\[\small
\begin{array}{ccc}
  {\color{brown}
    \inferrule[\textsc{Fac-Create-Pos}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{+ \ell \in pc} \\\\
                e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  & 
  {\color{gray}
    \inferrule[\textsc{Fac-Create-Neg}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{- \ell \in pc} \\\\
                e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  &
  {\color{purple}
    \inferrule[\textsc{Fac-Create-Split}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{\{+\ell, -\ell\} \cap pc = \varnothing} \\\\
                e_2, \rho, \sigma' \Downarrow_{pc \cup \{+\ell\}}^E \sigma'', v_1 \\\\
                e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-\ell\}}^E \sigma''', v_2 \and
                v = \formfacet{pc}{v_1}{v_2}}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
\end{array}
\]
